Mallows, Black-box combinatorial optimization, limited budget, ???

### 2020-10-21 paper/main.tex
fix table

            &                  & \mcolc{4}{Mean fitness (sd)} & \mcolc{2}{\multirow[b]{2.45}{*}{\shortstack{95\% CI for the\\mean difference}}} & \bf \multirow[b]{2.45}{*}{\shortstack{Mean FE\\CEGO}} & \mcolc{2}{Mean runtime} \\\cmidrule{3-6}\cmidrule(lr){9-10}

@@

    LOP     & N-t1d100.01      & (915.4)         & 76119.6          & 78696.6                 & (811.4)    & $[$1763.5,    & 3390.5$]$     & 111.8& 72.5 & 3.2  \\
    LOP     & N-t1d100.02      & (891.0)         & 76827.7          & 79686.5                 & (367.9)    & $[$2194.5,    & 3523.1$]$     & 110.7& 72.9 & 3.2  \\
    LOP     & N-t1d150.01      & (1647.9)        & 179508.3         & 187605.5                & (1906.9)   & $[$6420.3,    & 9774.1$]$     & 73.9 & 72.7 & 6.5  \\
    LOP     & N-t1d150.02      & (1196.2)        & 177592.8         & 184320.9                & (973.5)    & $[$5700.5,    & 7755.7$]$     & 74.1 & 73.2 & 6.5  \\
    LOP     & N-t1d200.01      & (1371.2)        & 323513.6         & 335391.1                & (2289.0)   & $[$10076.1,   & 13678.9$]$    & 55.6 & 73.2 & 10.7 \\
    LOP     & N-t1d200.02      & (2242.6)        & 319675.8         & 333149.5                & (2497.2)   & $[$11242.0,   & 15705.4$]$    & 56.5 & 73.7 & 10.6 \\
    LOP     & N-t2d150.01      & (563.5)         & 15297.7          & 24682.7                 & (976.6)    & $[$8622.2,    & 10147.8$]$    & 74.6 & 72.9 & 7.0  \\
    LOP     & N-t2d150.02      & (667.5)         & 14724.9          & 24250.8                 & (1354.9)   & $[$8495.1,    & 10556.7$]$    & 74.8 & 72.8 & 7.1  \\
    LOP     & N-t2d200.01      & (2001.0)        & 33465.2          & 57098.6                 & (4452.8)   & $[$20284.5,   & 26982.3$]$    & 56.3 & 73.3 & 11.2 \\
    LOP     & N-t2d200.02      & (2077.5)        & 35901.8          & 54895.6                 & (4589.7)   & $[$15539.1,   & 22448.5$]$    & 55.6 & 73.5 & 11.2 \\
    LOP     & N-p50-01         & (711.8)         & 21027.6          & 21431.2                 & (299.5)    & $[$-128.1,    & 935.3$]$      & 219.9& 72.3 & 0.9  \\
    LOP     & N-p50-02         & (596.4)         & 21613.6          & 22021.1                 & (275.6)    & $[$-42.5,     & 857.5$]$      & 217.3& 72.3 & 0.9  \\
    LOP     & N-atp111         & (15.4)          & 594.0            & 693.1                   & (10.3)     & $[$86.7,      & 111.5$]$      & 98.7 & 72.5 & 4.1  \\
    LOP     & N-atp134         & (21.3)          & 756.3            & 880.5                   & (18.6)     & $[$105.4,     & 143.0$]$      & 83.0 & 72.8 & 5.7  \\
    LOP     & N-be75eec\_150   & (58593.5)       & 1415208.5        & 1666193.1               & (72310.8)  & $[$188960.6,  & 313008.6$]$   & 74.0 & 72.9 & 6.9  \\
    LOP     & N-be75eec\_250   & (109756.7)      & 4431271.0        & 5214413.0               & (166701.4) & $[$649040.8,  & 917243.2$]$   & 44.9 & 73.7 & 15.5 \\
    LOP     & N-be75np\_150    & (80704.1)       & 3204878.3        & 3742444.0               & (88500.2)  & $[$457944.2,  & 617187.2$]$   & 74.2 & 72.9 & 6.9  \\
    LOP     & N-be75np\_250    & (260523.9)      & 9544754.9        & 10887427.8              & (159642.5) & $[$1136635.8, & 1548710.0$]$  & 45.3 & 74.0 & 15.5 \\
   PFSP     & rec05.txt        & (17.9)          & 1330.7           & 1317.9                  & (25.1)     & $[$-33.4,     & 7.8$]$        & 400.0& 38.9 & 0.1  \\
   PFSP     & rec13.txt        & (29.5)          & 2158.7           & 2128.2                  & (25.0)     & $[$-56.2,     & -4.8$]$       & 400.0& 38.9 & 0.1  \\
   PFSP     & rec19.txt        & (12.6)          & 2405.1           & 2398.6                  & (19.8)     & $[$-22.3,     & 9.3$]$        & 400.0& 82.1 & 0.3  \\
    QAP     & kra32.dat        & (4673.5)        & 116320.0         & 115907.0                & (4663.4)   & $[$-4799.3,   & 3973.3$]$     & 400.0& 95.8 & 0.3  \\
    QAP     & nug12.dat        & (17.3)          & 660.4            & 624.2                   & (26.3)     & $[$-57.3,     & -15.1$]$      & 400.0& 14.8 & 0.0  \\
    QAP     & nug30.dat        & (83.9)          & 7474.0           & 7486.8                  & (40.4)     & $[$-50.8,     & 76.4$]$       & 400.0& 84.3 & 0.3  \\
    QAP     & tho30.dat        & (4419.7)        & 191482.0         & 192416.0                & (2584.2)   & $[$-2527.0,   & 4395.0$]$     & 400.0& 85.1 & 0.3  \\

>>>>

            &                  & \mcolc{4}{Mean fitness (sd)} & \mcolc{2}{\multirow[b]{2.45}{*}{\shortstack{95\% CI for the\\mean difference}}} & \bf \multirow[b]{2.45}{*}{\shortstack{Mean FE\\CEGO}} & \mcolc{2}{Mean runtime} \\\cmidrule{3-6}\cmidrule(lr){10-11}

@@

    LOP     & N-t1d100.01      & 78696.6                 & (811.4)    & 76119.6   & (915.4)                & $[$1763.5,    & 3390.5$]$     & 111.8& 72.5 & 3.2  \\
    LOP     & N-t1d100.02      & 79686.5                 & (367.9)    & 76827.7   & (891.0)                & $[$2194.5,    & 3523.1$]$     & 110.7& 72.9 & 3.2  \\
    LOP     & N-t1d150.01      & 187605.5                & (1906.9)   & 179508.3  & (1647.9)               & $[$6420.3,    & 9774.1$]$     & 73.9 & 72.7 & 6.5  \\
    LOP     & N-t1d150.02      & 184320.9                & (973.5)    & 177592.8  & (1196.2)               & $[$5700.5,    & 7755.7$]$     & 74.1 & 73.2 & 6.5  \\
    LOP     & N-t1d200.01      & 335391.1                & (2289.0)   & 323513.6  & (1371.2)               & $[$10076.1,   & 13678.9$]$    & 55.6 & 73.2 & 10.7 \\
    LOP     & N-t1d200.02      & 333149.5                & (2497.2)   & 319675.8  & (2242.6)               & $[$11242.0,   & 15705.4$]$    & 56.5 & 73.7 & 10.6 \\
    LOP     & N-t2d150.01      & 24682.7                 & (976.6)    & 15297.7   & (563.5)                & $[$8622.2,    & 10147.8$]$    & 74.6 & 72.9 & 7.0  \\
    LOP     & N-t2d150.02      & 24250.8                 & (1354.9)   & 14724.9   & (667.5)                & $[$8495.1,    & 10556.7$]$    & 74.8 & 72.8 & 7.1  \\
    LOP     & N-t2d200.01      & 57098.6                 & (4452.8)   & 33465.2   & (2001.0)               & $[$20284.5,   & 26982.3$]$    & 56.3 & 73.3 & 11.2 \\
    LOP     & N-t2d200.02      & 54895.6                 & (4589.7)   & 35901.8   & (2077.5)               & $[$15539.1,   & 22448.5$]$    & 55.6 & 73.5 & 11.2 \\
    LOP     & N-p50-01         & 21431.2                 & (299.5)    & 21027.6   & (711.8)                & $[$-128.1,    & 935.3$]$      & 219.9& 72.3 & 0.9  \\
    LOP     & N-p50-02         & 22021.1                 & (275.6)    & 21613.6   & (596.4)                & $[$-42.5,     & 857.5$]$      & 217.3& 72.3 & 0.9  \\
    LOP     & N-atp111         & 693.1                   & (10.3)     & 594.0     & (15.4)                 & $[$86.7,      & 111.5$]$      & 98.7 & 72.5 & 4.1  \\
    LOP     & N-atp134         & 880.5                   & (18.6)     & 756.3     & (21.3)                 & $[$105.4,     & 143.0$]$      & 83.0 & 72.8 & 5.7  \\
    LOP     & N-be75eec\_150   & 1666193.1               & (72310.8)  & 1415208.5 & (58593.5)              & $[$188960.6,  & 313008.6$]$   & 74.0 & 72.9 & 6.9  \\
    LOP     & N-be75eec\_250   & 5214413.0               & (166701.4) & 4431271.0 & (109756.7)             & $[$649040.8,  & 917243.2$]$   & 44.9 & 73.7 & 15.5 \\
    LOP     & N-be75np\_150    & 3742444.0               & (88500.2)  & 3204878.3 & (80704.1)              & $[$457944.2,  & 617187.2$]$   & 74.2 & 72.9 & 6.9  \\
    LOP     & N-be75np\_250    & 10887427.8              & (159642.5) & 9544754.9 & (260523.9)             & $[$1136635.8, & 1548710.0$]$  & 45.3 & 74.0 & 15.5 \\
   PFSP     & rec05.txt        & 1317.9                  & (25.1)     & 1330.7    & (17.9)                 & $[$-33.4,     & 7.8$]$        & 400.0& 38.9 & 0.1  \\
   PFSP     & rec13.txt        & 2128.2                  & (25.0)     & 2158.7    & (29.5)                 & $[$-56.2,     & -4.8$]$       & 400.0& 38.9 & 0.1  \\
   PFSP     & rec19.txt        & 2398.6                  & (19.8)     & 2405.1    & (12.6)                 & $[$-22.3,     & 9.3$]$        & 400.0& 82.1 & 0.3  \\
    QAP     & kra32.dat        & 115907.0                & (4663.4)   & 116320.0  & (4673.5)               & $[$-4799.3,   & 3973.3$]$     & 400.0& 95.8 & 0.3  \\
    QAP     & nug12.dat        & 624.2                   & (26.3)     & 660.4     & (17.3)                 & $[$-57.3,     & -15.1$]$      & 400.0& 14.8 & 0.0  \\
    QAP     & nug30.dat        & 7486.8                  & (40.4)     & 7474.0    & (83.9)                 & $[$-50.8,     & 76.4$]$       & 400.0& 84.3 & 0.3  \\
    QAP     & tho30.dat        & 192416.0                & (2584.2)   & 191482.0  & (4419.7)               & $[$-2527.0,   & 4395.0$]$     & 400.0& 85.1 & 0.3  \\
